Compositional Certified Resource Bounds

### 2015-04-09 paper/main.tex
fix some phrasing

Generally, we observed that because the instrumented program
is structurally same as the original one, it is sufficient to prove
that the added assertions never fail to show that they have identical
resource consumption.  This can be piggybacked on standard
static-analysis tools.

>>>>

Generally, we observed that because the instrumented program
is structurally same as the original one, it is enough to prove
that the added assertions never fail in order to show the two programs
have identical resource consumption.  This can usually be piggybacked
on standard static-analysis tools.
